Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-01-21 Paper/paper.tex
updated AnalyzeSamples to include many new plots

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{What do we gain by using templates that include NS matter effects?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% \begin{figure*}
% \centering
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_NSLambdaBias_vs_SNR_q23.pdf}
% \caption{This figure is similar to the bottom row of
% Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}, with the difference that  we
% consider the NS tidal parameter $\Lambda$ here.}
% \label{fig:TT_NSLambdaBias_vs_SNR_q23}
% \end{figure*}
% % 
% \begin{figure*}
% \centering
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_NSLambdaCIWidth90_vs_SNR_q23.pdf}
% \caption{This figure is similar to the bottom row of
% Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}, with the difference that  
% we consider the NS tidal parameter $\Lambda$ here.}
% \label{fig:TT_NSLambdaCIWidth90_vs_SNR_q23}
% \end{figure*}
% % 
% \begin{figure*}
% \centering    
% \includegraphics[width=2\columnwidth]{plots-TT/TT_LambdaBiases_CI90_0_Lambda_SNR.png}
% \caption{This figure shows.}
% \label{fig:TT_LambdaBiases_CI90_0_Lambda_SNR}
% \end{figure*}
% 
\begin{figure*}
\centering    
\includegraphics[width=2.1\columnwidth]{plots-TT/TT_LambdaCIWidths68_3_Lambda_SNR.png}\\
\includegraphics[width=2.1\columnwidth]{plots-TT/TT_LambdaCIWidths90_0_Lambda_SNR.png}
\caption{This figure shows.}
\label{fig:TT_LambdaCIWidths90_0_Lambda_SNR}
\end{figure*}
% 
\begin{figure*}
\centering    
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI68_3.png}\\
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI90_0.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI90_0.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI90_0.png}
\caption{This figure shows.}
\label{fig:TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_CI90_0}
\end{figure*}
% 
\begin{figure*}
\centering    
\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR30_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR50_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR90_0_CI68_3.png}\\
\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR50_0_CI90_0.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR90_0_CI90_0.png}
\caption{This figure shows.}
\label{fig:TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{What do we gain by using templates that include NS matter effects?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% \begin{figure*}
% \centering
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_NSLambdaBias_vs_SNR_q23.pdf}
% \caption{This figure is similar to the bottom row of
% Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}, with the difference that  we
% consider the NS tidal parameter $\Lambda$ here.}
% \label{fig:TT_NSLambdaBias_vs_SNR_q23}
% \end{figure*}
% % 
% \begin{figure*}
% \centering
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_NSLambdaCIWidth90_vs_SNR_q23.pdf}
% \caption{This figure is similar to the bottom row of
% Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}, with the difference that  
% we consider the NS tidal parameter $\Lambda$ here.}
% \label{fig:TT_NSLambdaCIWidth90_vs_SNR_q23}
% \end{figure*}
% % 
% \begin{figure*}
% \centering    
% \includegraphics[width=2\columnwidth]{plots-TT/TT_LambdaBiases_CI90_0_Lambda_SNR.png}
% \caption{This figure shows.}
% \label{fig:TT_LambdaBiases_CI90_0_Lambda_SNR}
% \end{figure*}

\begin{figure*}
\centering    
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI68_3.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI68_3.png}\\
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI90_0.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI90_0.png}
\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI90_0.png}
\caption{This figure shows.}
\label{fig:TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_CI90_0}
\end{figure*}

% 
\begin{figure*}
\centering    
\includegraphics[width=2.1\columnwidth]{plots-TT/TTLambdaCIWidths68_3_Lambda_SNR.png}\\
\includegraphics[width=2.1\columnwidth]{plots-TT/TTLambdaCIWidths90_0_Lambda_SNR.png}
\caption{This figure shows.}
\label{fig:TT_LambdaCIWidths90_0_Lambda_SNR}
\end{figure*}
% 
%\begin{figure*}
%\centering    
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI68_3.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI68_3.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI68_3.png}\\
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda500_0_CI90_0.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda800_0_CI90_0.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_Lambda1000_0_CI90_0.png}
%\caption{This figure shows.}
%\label{fig:TT_SNRThresholdForLambdaMeasurement_BHspin_MassRatio_CI90_0}
%\end{figure*}
%% 
%\begin{figure*}
%\centering    
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR30_0_CI68_3.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR50_0_CI68_3.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR90_0_CI68_3.png}\\
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR50_0_CI90_0.png}
%\includegraphics[width=.65\columnwidth]{plots-TT/TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass_SNR90_0_CI90_0.png}
%\caption{This figure shows.}
%\label{fig:TT_LambdaThresholdForLambdaMeasurement_BHspin_BHmass}
%\end{figure*}

@@
